True versus apparent shapes of astrophysical bow shocks

### 2017-05-26 Stellar-Bowshocks-2017/mipsgal-summary-stats-table-body.tex
Discussion and tweaking of box plot figure

%%% 2017-04-19 13:16:10.731012

@@

	  & & \multicolumn{2}{c}{Mean} & \multicolumn{2}{c}{Std.\ Dev.} & \multicolumn{2}{c}{Obs.\ Disp.} & \multicolumn{2}{c @{\quad\quad\quad}}{s.e.m.} & \multicolumn{3}{c @{\quad} }{\dotfill Effect sizes\dotfill } & \multicolumn{3}{c}{\dotfill Non-parametric test \(p\)-values  \dotfill} \\ 

@@

	  \midrule\multicolumn{10}{@{} l @{\quad\quad\quad}}{\itshape Median split of continuous variables \dotfill}\\

@@

Faint/bright & \(R_{90}\) & 1.677 & 1.768 & 0.269 & 0.316 & 0.231 & 0.236 & 0.025 & 0.03 & \itshape 0.174 & \itshape 0.308 & 1.175 & \itshape 0.0215 & \itshape 0.0235 & 0.125\\
\(H\) magnitude & \(\Delta R_{90}\) & 0.183 & 0.198 & 0.161 & 0.163 &   &   & 0.015 & 0.015 & 0.07 & 0.093 & 1.013 & 0.538 & 0.365 & 0.761\\
\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(R_{c}\) & 1.655 & 1.917 & 0.631 & 1.045 & 0.097 & 0.078 & 0.059 & 0.098 & 0.123 & 0.303 & \itshape 1.654 & 0.123 & 0.111 & \itshape 0.0335\\

@@

Low/high & \(R_{90}\) & 1.707 & 1.739 & 0.25 & 0.336 & 0.256 & 0.212 & 0.024 & 0.031 & 0.061 & 0.11 & \bfseries 1.342 & \itshape 0.0281 & \itshape 0.428 & \bfseries 0.00139\\
bow shock size, \(R_0\) & \(\Delta R_{90}\) & 0.175 & 0.204 & 0.157 & 0.165 &   &   & 0.015 & 0.015 & 0.091 & 0.176 & 1.054 & 0.103 & 0.238 & 0.193\\
\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(R_{c}\) & 1.766 & 1.803 & 0.975 & 0.755 & 0.114 & 0.062 & 0.092 & 0.071 & 0.1 & 0.043 & 0.774 & 0.228 & 0.192 & 0.599\\

@@

Low/high & \(R_{90}\) & 1.703 & 1.742 & 0.267 & 0.323 & 0.233 & 0.235 & 0.025 & 0.03 & 0.04 & 0.132 & 1.213 & 0.554 & 0.602 & 0.123\\
extinction, \(A_K\) & \(\Delta R_{90}\) & 0.186 & 0.195 & 0.138 & 0.183 &   &   & 0.013 & 0.017 & -0.039 & 0.057 & 1.326 & 0.301 & 0.61 & 0.112\\
\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(R_{c}\) & 1.725 & 1.846 & 0.822 & 0.917 & 0.091 & 0.085 & 0.077 & 0.086 & 0.082 & 0.139 & 1.116 & 0.219 & 0.285 & 0.982\\

@@

Low/high & \(R_{90}\) & 1.722 & 1.724 & 0.328 & 0.261 & 0.234 & 0.234 & 0.031 & 0.024 & 0.02 & 0.008 & 0.796 & 0.308 & 0.795 & 0.0534\\
\(\vert{}b\vert\) & \(\Delta R_{90}\) & 0.188 & 0.191 & 0.161 & 0.162 &   &   & 0.015 & 0.015 & 0.009 & 0.021 & 1.005 & 0.964 & 0.907 & 0.694\\
\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(R_{c}\) & 1.706 & 1.862 & 0.727 & 0.988 & 0.085 & 0.091 & 0.068 & 0.092 & 0.069 & 0.181 & 1.358 & 0.19 & 0.368 & 0.0842\\

@@

High/low & \(R_{90}\) & 1.734 & 1.707 & 0.279 & 0.321 & 0.241 & 0.223 & 0.024 & 0.034 & -0.049 & -0.093 & 1.152 & 0.361 & 0.532 & 0.159\\
\(\cos \ell\) & \(\Delta R_{90}\) & 0.182 & 0.201 & 0.155 & 0.171 &   &   & 0.013 & 0.018 & 0.054 & 0.122 & 1.1 & 0.604 & 0.491 & 0.365\\
\(n_{\text{A}}, n_{\text{B}} = 137, 90\) & \(R_{c}\) & 1.807 & 1.751 & 0.946 & 0.742 & 0.09 & 0.084 & 0.081 & 0.078 & -0.0 & -0.064 & 0.785 & 1.03 & 0.999 & 0.549\\

@@

\multicolumn{10}{@{} l @{\quad\quad\quad}}{\itshape Categorical variables \dotfill}\\

@@

Environment: & \(R_{90}\) & 1.735 & 1.693 & 0.283 & 0.338 & 0.238 & 0.218 & 0.022 & 0.053 & -0.07 & -0.142 & 1.194 & 0.603 & 0.49 & 0.392\\
Isolated vs Facing & \(\Delta R_{90}\) & 0.19 & 0.195 & 0.161 & 0.172 &   &   & 0.012 & 0.027 & -0.019 & 0.034 & 1.066 & 0.507 & 0.85 & 0.438\\
\(n_{\text{A}}, n_{\text{B}} = 170, 41\) & \(R_{c}\) & 1.757 & 1.852 & 0.854 & 0.899 & 0.087 & 0.083 & 0.066 & 0.14 & 0.042 & 0.11 & 1.053 & 0.713 & 0.676 & 0.377\\

@@

Environment: & \(R_{90}\) & 1.735 & 1.68 & 0.283 & 0.309 & 0.238 & 0.233 & 0.022 & 0.077 & -0.13 & -0.193 & 1.092 & 0.518 & 0.391 & 0.782\\
Isolated vs \hii & \(\Delta R_{90}\) & 0.19 & 0.175 & 0.161 & 0.138 &   &   & 0.012 & 0.034 & -0.048 & -0.095 & 0.855 & 0.932 & 0.754 & 0.799\\
\(n_{\text{A}}, n_{\text{B}} = 170, 16\) & \(R_{c}\) & 1.757 & 1.907 & 0.854 & 0.955 & 0.087 & 0.105 & 0.066 & 0.239 & 0.024 & 0.174 & 1.118 & 0.496 & 0.875 & 0.255\\

@@

Single/multiple & \(R_{90}\) & 1.709 & 1.762 & 0.289 & 0.315 & 0.23 & 0.243 & 0.022 & 0.041 & 0.074 & 0.177 & 1.09 & 0.342 & 0.396 & 0.338\\
source candidate & \(\Delta R_{90}\) & 0.184 & 0.206 & 0.162 & 0.16 &   &   & 0.013 & 0.021 & 0.093 & 0.136 & 0.987 & 0.421 & 0.284 & 0.97\\
\(n_{\text{A}}, n_{\text{B}} = 167, 60\) & \(R_{c}\) & 1.767 & 1.833 & 0.825 & 0.988 & 0.09 & 0.08 & 0.064 & 0.128 & 0.027 & 0.076 & 1.198 & 0.999 & 0.756 & 0.605\\

@@

With/without & \(R_{90}\) & 1.734 & 1.721 & 0.289 & 0.298 & 0.223 & 0.237 & 0.043 & 0.022 & -0.042 & -0.044 & 1.031 & 0.595 & 0.667 & 0.563\\
\SI{8}{\um} emission & \(\Delta R_{90}\) & 0.203 & 0.186 & 0.205 & 0.149 &   &   & 0.031 & 0.011 & 0.021 & -0.106 & 0.726 & 0.765 & 0.826 & 0.219\\
\(n_{\text{A}}, n_{\text{B}} = 45, 182\) & \(R_{c}\) & 1.714 & 1.802 & 0.598 & 0.926 & 0.091 & 0.087 & 0.089 & 0.069 & -0.012 & 0.101 & 1.547 & 0.824 & 0.904 & 0.2\\

@@

MIPS vs Orion & \(R_{90}\) & 1.723 & 2.418 & 0.297 & 0.811 &   &   & 0.02 & 0.191 & \bfseries 0.7 & \bfseries 1.928 & \bfseries 2.735 & \bfseries 8.02e-06 & \bfseries 7.84e-07 & \bfseries 6.41e-06\\
 & \(\Delta R_{90}\) & 0.19 & 0.701 & 0.162 & 0.532 &   &   & 0.011 & 0.148 & \bfseries 0.689 & \bfseries 2.553 & \bfseries 3.29 & \bfseries 9.94e-06 & \bfseries 3e-05 & \bfseries 2.42e-10\\
\(n_{\text{A}}, n_{\text{B}} = 227, 18\) & \(R_{c}\) & 1.784 & 2.639 & 0.871 & 1.302 &   &   & 0.058 & 0.307 & \bfseries 0.516 & \bfseries 0.94 & 1.495 & \bfseries 0.000505 & \bfseries 0.000273 & 0.12\\

@@

MIPS vs RSG & \(R_{90}\) & 1.723 & 1.386 & 0.297 & 0.122 &   &   & 0.02 & 0.046 & \bfseries -0.756 & \bfseries -1.152 & 0.412 & \bfseries 0.000494 & \bfseries 0.000671 & 0.0573\\
 & \(\Delta R_{90}\) & 0.19 & 0.23 & 0.162 & 0.308 &   &   & 0.011 & 0.126 & -0.116 & 0.242 & 1.904 & 0.373 & 0.63 & 0.26\\
\(n_{\text{A}}, n_{\text{B}} = 227, 7\) & \(R_{c}\) & 1.784 & 1.426 & 0.871 & 0.079 &   &   & 0.058 & 0.03 & -0.201 & -0.418 & 0.091 & 0.0742 & 0.367 & 0.0505

>>>>

%%% 2017-05-26 13:27:55.244997

@@

	  & {Dependent} & \multicolumn{2}{c}{Mean} & \multicolumn{2}{c}{Std.\ Dev.} & \multicolumn{2}{c}{Obs.\ Disp.} & \multicolumn{2}{c @{\quad\quad\quad}}{s.e.m.} & \multicolumn{3}{c @{\quad} }{\dotfill Effect sizes\dotfill } & \multicolumn{3}{c}{\dotfill Non-parametric test \(p\)-values  \dotfill} \\ 

@@

	  \midrule\multicolumn{10}{@{} l @{\quad\quad\quad}}{\itshape Median split of continuous independent variables \dotfill}\\

@@

Faint/bright & \(R_{90} / R_{0}\) & 1.677 & 1.768 & 0.269 & 0.316 & 0.231 & 0.236 & 0.025 & 0.03 & \itshape 0.174 & \itshape 0.308 & 1.175 & \itshape 0.0215 & \itshape 0.0235 & 0.125\\
\(H\) magnitude & \(\Delta R_{90} / R_{90}\) & 0.183 & 0.198 & 0.161 & 0.163 &   &   & 0.015 & 0.015 & 0.07 & 0.093 & 1.013 & 0.538 & 0.365 & 0.761\\
\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(R_{c} / R_{0}\) & 1.655 & 1.917 & 0.631 & 1.045 & 0.097 & 0.078 & 0.059 & 0.098 & 0.123 & 0.303 & \itshape 1.654 & 0.123 & 0.111 & \itshape 0.0335\\

@@

Low/high & \(R_{90} / R_{0}\) & 1.707 & 1.739 & 0.25 & 0.336 & 0.256 & 0.212 & 0.024 & 0.031 & 0.061 & 0.11 & \bfseries 1.342 & \itshape 0.0281 & 0.428 & \bfseries 0.00139\\
bow shock size, \(R_0\) & \(\Delta R_{90} / R_{90}\) & 0.175 & 0.204 & 0.157 & 0.165 &   &   & 0.015 & 0.015 & 0.091 & 0.176 & 1.054 & 0.103 & 0.238 & 0.193\\
\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(R_{c} / R_{0}\) & 1.766 & 1.803 & 0.975 & 0.755 & 0.114 & 0.062 & 0.092 & 0.071 & 0.1 & 0.043 & 0.774 & 0.228 & 0.192 & 0.599\\

@@

Low/high & \(R_{90} / R_{0}\) & 1.703 & 1.742 & 0.267 & 0.323 & 0.233 & 0.235 & 0.025 & 0.03 & 0.04 & 0.132 & 1.213 & 0.554 & 0.602 & 0.123\\
extinction, \(A_K\) & \(\Delta R_{90} / R_{90}\) & 0.186 & 0.195 & 0.138 & 0.183 &   &   & 0.013 & 0.017 & -0.039 & 0.057 & 1.326 & 0.301 & 0.61 & 0.112\\
\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(R_{c} / R_{0}\) & 1.725 & 1.846 & 0.822 & 0.917 & 0.091 & 0.085 & 0.077 & 0.086 & 0.082 & 0.139 & 1.116 & 0.219 & 0.285 & 0.982\\

@@

Low/high & \(R_{90} / R_{0}\) & 1.722 & 1.724 & 0.328 & 0.261 & 0.234 & 0.234 & 0.031 & 0.024 & 0.02 & 0.008 & 0.796 & 0.308 & 0.795 & 0.0534\\
\(\vert{}b\vert\) & \(\Delta R_{90} / R_{90}\) & 0.188 & 0.191 & 0.161 & 0.162 &   &   & 0.015 & 0.015 & 0.009 & 0.021 & 1.005 & 0.964 & 0.907 & 0.694\\
\(n_{\text{A}} =  n_{\text{B}} = 113\) & \(R_{c} / R_{0}\) & 1.706 & 1.862 & 0.727 & 0.988 & 0.085 & 0.091 & 0.068 & 0.092 & 0.069 & 0.181 & 1.358 & 0.19 & 0.368 & 0.0842\\

@@

High/low & \(R_{90} / R_{0}\) & 1.734 & 1.707 & 0.279 & 0.321 & 0.241 & 0.223 & 0.024 & 0.034 & -0.049 & -0.093 & 1.152 & 0.361 & 0.532 & 0.159\\
\(\cos \ell\) & \(\Delta R_{90} / R_{90}\) & 0.182 & 0.201 & 0.155 & 0.171 &   &   & 0.013 & 0.018 & 0.054 & 0.122 & 1.1 & 0.604 & 0.491 & 0.365\\
\(n_{\text{A}}, n_{\text{B}} = 137, 90\) & \(R_{c} / R_{0}\) & 1.807 & 1.751 & 0.946 & 0.742 & 0.09 & 0.084 & 0.081 & 0.078 & -0.0 & -0.064 & 0.785 & 1.03 & 0.999 & 0.549\\

@@

\multicolumn{10}{@{} l @{\quad\quad\quad}}{\itshape Categorical independent variables \dotfill}\\

@@

Environment: & \(R_{90} / R_{0}\) & 1.735 & 1.693 & 0.283 & 0.338 & 0.238 & 0.218 & 0.022 & 0.053 & -0.07 & -0.142 & 1.194 & 0.603 & 0.49 & 0.392\\
Isolated vs Facing & \(\Delta R_{90} / R_{90}\) & 0.19 & 0.195 & 0.161 & 0.172 &   &   & 0.012 & 0.027 & -0.019 & 0.034 & 1.066 & 0.507 & 0.85 & 0.438\\
\(n_{\text{A}}, n_{\text{B}} = 170, 41\) & \(R_{c} / R_{0}\) & 1.757 & 1.852 & 0.854 & 0.899 & 0.087 & 0.083 & 0.066 & 0.14 & 0.042 & 0.11 & 1.053 & 0.713 & 0.676 & 0.377\\

@@

Environment: & \(R_{90} / R_{0}\) & 1.735 & 1.68 & 0.283 & 0.309 & 0.238 & 0.233 & 0.022 & 0.077 & -0.13 & -0.193 & 1.092 & 0.518 & 0.391 & 0.782\\
Isolated vs \hii & \(\Delta R_{90} / R_{90}\) & 0.19 & 0.175 & 0.161 & 0.138 &   &   & 0.012 & 0.034 & -0.048 & -0.095 & 0.855 & 0.932 & 0.754 & 0.799\\
\(n_{\text{A}}, n_{\text{B}} = 170, 16\) & \(R_{c} / R_{0}\) & 1.757 & 1.907 & 0.854 & 0.955 & 0.087 & 0.105 & 0.066 & 0.239 & 0.024 & 0.174 & 1.118 & 0.496 & 0.875 & 0.255\\

@@

Single/multiple & \(R_{90} / R_{0}\) & 1.709 & 1.762 & 0.289 & 0.315 & 0.23 & 0.243 & 0.022 & 0.041 & 0.074 & 0.177 & 1.09 & 0.342 & 0.396 & 0.338\\
source candidate & \(\Delta R_{90} / R_{90}\) & 0.184 & 0.206 & 0.162 & 0.16 &   &   & 0.013 & 0.021 & 0.093 & 0.136 & 0.987 & 0.421 & 0.284 & 0.97\\
\(n_{\text{A}}, n_{\text{B}} = 167, 60\) & \(R_{c} / R_{0}\) & 1.767 & 1.833 & 0.825 & 0.988 & 0.09 & 0.08 & 0.064 & 0.128 & 0.027 & 0.076 & 1.198 & 0.999 & 0.756 & 0.605\\

@@

With/without & \(R_{90} / R_{0}\) & 1.734 & 1.721 & 0.289 & 0.298 & 0.223 & 0.237 & 0.043 & 0.022 & -0.042 & -0.044 & 1.031 & 0.595 & 0.667 & 0.563\\
\SI{8}{\um} emission & \(\Delta R_{90} / R_{90}\) & 0.203 & 0.186 & 0.205 & 0.149 &   &   & 0.031 & 0.011 & 0.021 & -0.106 & 0.726 & 0.765 & 0.826 & 0.219\\
\(n_{\text{A}}, n_{\text{B}} = 45, 182\) & \(R_{c} / R_{0}\) & 1.714 & 1.802 & 0.598 & 0.926 & 0.091 & 0.087 & 0.089 & 0.069 & -0.012 & 0.101 & 1.547 & 0.824 & 0.904 & 0.2\\
3-star vs (4+5)-star & \(R_{90} / R_{0}\) & 1.661 & 1.812 & 0.288 & 0.286 & 0.247 & 0.216 & 0.025 & 0.029 & \bfseries 0.328 & \bfseries 0.525 & 0.99 & \bfseries 8.23e-05 & \bfseries 2.63e-05 & 0.403\\
 & \(\Delta R_{90} / R_{90}\) & 0.189 & 0.19 & 0.162 & 0.161 &   &   & 0.014 & 0.017 & -0.007 & 0.009 & 0.994 & 0.809 & 0.927 & 0.561\\
\(n_{\text{A}}, n_{\text{B}} = 133, 94\) & \(R_{c} / R_{0}\) & 1.632 & 2.0 & 0.91 & 0.764 & 0.106 & 0.061 & 0.079 & 0.079 & \bfseries 0.386 & \bfseries 0.431 & 0.84 & \bfseries 1.47e-05 & \bfseries 7.66e-07 & 0.762\\

@@

MIPS vs Orion & \(R_{90} / R_{0}\) & 1.723 & 2.418 & 0.297 & 0.811 &   &   & 0.02 & 0.191 & \bfseries 0.7 & \bfseries 1.928 & \bfseries 2.735 & \bfseries 8.02e-06 & \bfseries 7.84e-07 & \bfseries 6.41e-06\\
 & \(\Delta R_{90} / R_{90}\) & 0.19 & 0.701 & 0.162 & 0.532 &   &   & 0.011 & 0.148 & \bfseries 0.689 & \bfseries 2.553 & \bfseries 3.29 & \bfseries 9.94e-06 & \bfseries 3e-05 & \bfseries 2.42e-10\\
\(n_{\text{A}}, n_{\text{B}} = 227, 18\) & \(R_{c} / R_{0}\) & 1.784 & 2.639 & 0.871 & 1.302 &   &   & 0.058 & 0.307 & \bfseries 0.516 & \bfseries 0.94 & 1.495 & \bfseries 0.000505 & \bfseries 0.000273 & 0.12\\

@@

MIPS vs RSG & \(R_{90} / R_{0}\) & 1.723 & 1.386 & 0.297 & 0.122 &   &   & 0.02 & 0.046 & \bfseries -0.756 & \bfseries -1.152 & 0.412 & \bfseries 0.000494 & \bfseries 0.000671 & 0.0573\\
 & \(\Delta R_{90} / R_{90}\) & 0.19 & 0.23 & 0.162 & 0.308 &   &   & 0.011 & 0.126 & -0.116 & 0.242 & 1.904 & 0.373 & 0.63 & 0.26\\
\(n_{\text{A}}, n_{\text{B}} = 227, 7\) & \(R_{c} / R_{0}\) & 1.784 & 1.426 & 0.871 & 0.079 &   &   & 0.058 & 0.03 & -0.201 & -0.418 & 0.091 & 0.0742 & 0.367 & 0.0505

### 2017-05-26 papers/Paper1/quadrics-appendix.tex
Discussion and tweaking of box plot figure

% Landscape table needs to go on its own page, so we need to manually
% adjust the section counter so that it will ``belong'' to the next
% section
\addtocounter{section}{1}
\sisetup{detect-all=true, detect-inline-weight=math}
\sisetup{round-mode=figures, round-precision=2}
\begin{landscape}
\begin{table}
  \setlength\tabcolsep{3pt}
  \caption{Results of all statistical tests performed on observed bow shock shape parameters. Significant correlations are shown in \textbf{bold}, marginally significant correlations in \textit{italic}}
  \label{tab:big-p}
  \input{figs/mipsgal-summary-stats-table-body.tex}
\end{table}
\end{landscape}
\begin{table}
  \contcaption{Results of all statistical tests performed on observed
    bow shock shape parameters.}
  \begin{tabular}{p{0.9\linewidth}}
    \toprule
    \textit{Description of columns:}
    (Col.~1)~How the two A/B source sub-samples are defined, also giving the size of each sub-sample, \(n_{\text{A}}\) and~\(n_{\text{B}}\).
    (Col.~2)~Dependent variable whose distribution is compared between the two sub-samples.
    (Cols.~3--6)~Mean and standard deviation, \(\sigma\), of the dependent variable for each of the two sub-samples.
    (Cols.~7--8)~Mean over each sub-sample of the observational dispersion (\(\epsilon\), standard deviation) of radii that contribute to the dependent variable for each individual source.
    (Cols.~9--10)~``Standard error of the mean'' (s.e.m.) of the dependent variable for each of the two sub-samples. 
    (Cols.~11--13)~Standardized ``effect sizes'', which are dimensionless measures of the difference in the distribution of the dependent variable between the two sub-samples.
    (Col.~11)~Rank biserial correlation coefficient \citep{Cureton:1956a}, which is obtained by considering all \(n_{\text{A}} n_{\text{B}}\) pair-wise comparisons of the dependent variable between a source in sub-sample~A and a source in sub-sample~B.  It is the difference between the fraction of such comparisons ``won'' by sub-sample~A and those ``won'' by sub-sample~B, and thus may vary between \(-1\) and \(+1\). 
    (Col.~12)~Cohen's \(d\), which is a dimensionless mean difference: \(d = (\langle \text{A} \rangle - \langle \text{B} \rangle) / \sigma_{\text{pool}} \), where \(\sigma_{\text{pool}} = (n_{\text{A}} \sigma_{\text{A}}^2 + n_{\text{B}} \sigma_{\text{B}}^2)^{1/2} / \sqrt{n_{\text{A}} + n_{\text{B}}}\) is the pooled standard deviation.
    (Col.~13)~Ratio of standard deviations between the two sub-samples.
    (Cols.~14--16)~Probabilities (\(p\)-values) of the two sub-samples being as different as observed if they were to be drawn from the same population, according to three different non-parametric tests.
    (Col.~14)~Anderson--Darling 2-sample test, which is a general test of similarity between two distributions that is designed to retain sensitivity to differences in the tails of the distributions.
    (Col.~15)~Mann--Whitney--Wilcoxon \(U\) test \citep{Mann:1947a}, which is sensitive 
    (Col.~16)~Brown--Forsythe test for equality of variance \citep{Brown:1974a}
    \\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

% Landscape table needs to go on its own page, so we need to manually
% adjust the section counter so that it will ``belong'' to the next
% section
\addtocounter{section}{1}
\sisetup{detect-all=true, detect-inline-weight=math}
\sisetup{round-mode=figures, round-precision=2}
\begin{landscape}
\begin{table}
  \setlength\tabcolsep{3pt}
  \caption{Results of all statistical tests performed on observed bow shock shape parameters. Significant correlations are shown in \textbf{bold}, marginally significant correlations in \textit{italic}}
  \label{tab:big-p}
  \input{figs/mipsgal-summary-stats-table-body.tex}
\end{table}
\end{landscape}
\begin{table}
  \contcaption{Results of all statistical tests performed on observed
    bow shock shape parameters.}
  \begin{tabular}{p{0.9\linewidth}}
    \toprule
    \textit{Description of columns:}
    (Col.~1)~How the two A/B source sub-samples are defined, also giving the size of each sub-sample, \(n_{\text{A}}\) and~\(n_{\text{B}}\).
    (Col.~2)~Dependent variable whose distribution is compared between the two sub-samples.
    (Cols.~3--6)~Mean and standard deviation, \(\sigma\), of the dependent variable for each of the two sub-samples.
    (Cols.~7--8)~Mean over each sub-sample of the observational dispersion (\(\epsilon\), standard deviation) of radii that contribute to the dependent variable for each individual source, as in steps~\ref{step:R0} and \ref{step:R90} of \S~\ref{sec:autom-trac-fitt}.  Note that in the case of \(R_c\), this is \(\epsilon(R_0)\), and so is not a direct measure of the observational uncertainty in \(R_c\). 
    (Cols.~9--10)~``Standard error of the mean'' (s.e.m.) of the dependent variable for each of the two sub-samples. 
    (Cols.~11--13)~Standardized ``effect sizes'', which are dimensionless measures of the difference in the distribution of the dependent variable between the two sub-samples.
    (Col.~11)~Rank biserial correlation coefficient \citep{Cureton:1956a}, which is obtained by considering all \(n_{\text{A}} n_{\text{B}}\) pair-wise comparisons of the dependent variable between a source in sub-sample~A and a source in sub-sample~B.  It is the difference between the fraction of such comparisons ``won'' by sub-sample~A and those ``won'' by sub-sample~B, and thus may vary between \(-1\) and \(+1\). 
    (Col.~12)~Cohen's \(d\), which is a dimensionless mean difference: \(d = (\langle \text{A} \rangle - \langle \text{B} \rangle) / \sigma_{\text{pool}} \), where \(\sigma_{\text{pool}} = (n_{\text{A}} \sigma_{\text{A}}^2 + n_{\text{B}} \sigma_{\text{B}}^2)^{1/2} / \sqrt{n_{\text{A}} + n_{\text{B}}}\) is the pooled standard deviation.
    (Col.~13)~Ratio of standard deviations between the two sub-samples.
    (Cols.~14--16)~Probabilities (\(p\)-values) of the two sub-samples being as different as observed if they were to be drawn from the same population, according to three different non-parametric tests.
    (Col.~14)~Anderson--Darling 2-sample test, which is a general test of similarity between two distributions that is designed to retain sensitivity to differences in the tails of the distributions.
    (Col.~15)~Mann--Whitney--Wilcoxon \(U\) test \citep{Mann:1947a}, which is sensitive 
    (Col.~16)~Brown--Forsythe test for equality of variance \citep{Brown:1974a}
    \\
    \bottomrule
  \end{tabular}
\end{table}
